---
title: "DSE 511 Question List"
format: html
editor: visual
---

## System Setup

```{r, warning = FALSE, message = FALSE}
library(readr)
library(arrow)
library(dplyr)
library(ggplot2)

# load data
complaint_data <- read_parquet("../raw_data/complaint_data_2019_2024.parquet.gz")
```

## Q1 - Are more complaints happening over time?

Answer: They are actually decreasing as time goes on; whether that's because the new cars have just been on the road less is something to be answered.

```{r}
# aggregate
year_complaint_count <- complaint_data |> 
  group_by(model_year) |> 
  count()

# plot
ggplot(year_complaint_count, aes(x = model_year, y = n)) +
  geom_col(fill = "blue") +
  scale_x_continuous(
    breaks = seq(min(year_complaint_count$model_year),
                 max(year_complaint_count$model_year),
                 by = 1)
  ) +
  labs(
    title = "Complaints by Model Year",
    x = "Model Year",
    y = "Number of Complaints"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )
```

------------------------------------------------------------------------

## Q2 - Which parent companies receive the most complaints?

Answer:

```{r}


```

### Q2.1 - How do the complaints for parent companies trend over time?

Answer:

```{r}

```

------------------------------------------------------------------------

## Q3 - Which components receive the most complaints?

Answer:

```{r}

```

### Q3.1 - How do the complaints for components trend over time?

Answer:

```{r}

```

### Q3.2 - How do the complaints for popular components trend over time?

Answer:

```{r}

```

### Q3.3 - What topics are most common for the most popular components?

Answer:

```{r}

```

------------------------------------------------------------------------

## Q4 - How do complaints around components and parent companies change over time spatially in the embedding space?

Answer:

```{r}

```

------------------------------------------------------------------------

## Q5 - Are new cars getting worse?

Answer:

```{r}

```
